---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->


```{r, include = FALSE}
knitr::opts_chunk$set(collapse  = TRUE,
                      comment   = "#>",
                      fig.path  = "man/figures/",
                      out.width = "100%")
```



# spatialews_biocom


<!-- badges: start -->
[![License: GPL (>= 2)](https://img.shields.io/badge/License-GPL%20%28%3E%3D%202%29-blue.svg)](https://choosealicense.com/licenses/gpl-2.0/)
[![Dependencies](https://img.shields.io/badge/dependencies-2/94-green?style=flat)](#)
<!-- badges: end -->


Research Compendium of the project **Spatial metrics calculation in the Biocom data set**


### How to cite

Please cite this compendium as: 

> **Sonia Kéfi and Alexandre Génin. Code associated with the paper 'Dryland resilience to aridity is associated with self-organized vegetation patchiness'**



### Content

This repository is structured as follow:

- [`data/`](https://github.com/skefi/spatialews_biocom/tree/master/raw-data):
contains raw data required to perform analyses (model and real data)

- [`R/`](https://github.com/skefi/spatialews_biocom/tree/master/R):
contains R functions allowing to prepare the data and calculate the spatial metrics in the model and in the data

- [`outputs/`](https://github.com/skefi/spatialews_biocom/tree/master/outputs):
contains the results created during the workflow

- [`analyses/`](https://github.com/skefi/spatialews_biocom/tree/master/analyses/):
contains R scripts to plot the figures

- [`figures/`](https://github.com/skefi/spatialews_biocom/tree/master/figures):
contains the figures created during the workflow

- [`man/`](https://github.com/skefi/spatialews_biocom/tree/master/man):
contains help files of R functions

- [`DESCRIPTION`](https://github.com/skefi/spatialews_biocom/tree/master/DESCRIPTION):
contains project metadata (author, date, dependencies, etc.)

- [`make.R`](https://github.com/skefi/spatialews_biocom/tree/master/make.R):
main R script to run the entire project by calling each R script stored in the `analyses/` folder



### Usage

Clone the repository, open spatialews_biocom.Rproj with R/Rstudio. 

To calculate the spatial metrics from the the real images (that are in `data/data_CA`) and from data generated by the model (that are in `data/data_images_biocom`), run:

```{r eval = FALSE}
source("make.R")
```

This generates result files that are saved in the folder `outputs`. In particular, `biocom-grps.rda` contains information about the field sites, `indics-data.rda` contains a set of spatial metrics measured on each of the real images, and `indics-model.rda` contains the same set of spatial metrics measured on the images generated by the model. The files `trends_model.rda`, `trends_one_group.rda`, `trends_two_groups.rda` and `trends_three_groups.rda` contain the trends (i.e. slopes) of each of the spatial metrics along the stress gradient (aridity in the data, parameter b in the model).

Using these files, code available in the folder `analyses` allows performing additional analyses and plotting the figures of the paper. 

The `plot_fig.R` files allow generating the figures of the paper. The files `clustering_analyses.R` and `compare_groups.R` perform additional analyses. 




### Notes

- All required packages, listed in the `DESCRIPTION` file, will be installed (if necessary)
- All required packages and R functions will be loaded
- Some analyses listed in the `make.R` might take time
